---
title: "DataScienceHTML"
author: "Chris Hill"
format: html
editor: visual
editor_options: 
  chunk_output_type: console
---

## What do you think being a data scientist is about?

I believe data science is a discipline that empowers people to transform raw data into meaningful insights. Thereby, enabling us to communicate complex ideas and create intriguing narratives that drive informed decision-making within a relevant system.

## What differences/similarities do you see between data scientists and statisticians? *(Use a markdown list at some point)*

-   I feel that statisticians emphasize more theory, while data scientists are interested in integrating technological tools like machine learning and building useful models.
-   Both aim to derive insights, but data scientists seem to focus more on practical applications as a general notion.

## How do you view yourself in relation to these two areas?

Working as an engineer, I align more with the applied sciences. However, I have decided to invest in building a strong foundation in the theory behind the tools we use. In my career, stakeholders often ask "why?" and I found myself lacking the answers. I realized I was using tools to communicate ideas without fully understanding their underlying principles, just because they met certain criteria. I was unable to communicate the necessity of an analysis on a deeper level.

## Create an R code chunk to determine the class, type, and structure of the object y

```{r}
y <- density(iris$Petal.Width)
class(y)
typeof(y)
str(y)
```

## Create an R code chunk that uses the plot function on y. Hide the R code in the final document by setting echo to false.

```{r}
#| echo=FALSE

plot(y)
```


 